---
title: "Report for exploratory reporting"
format: docx
---

```{r, echo=F, warning=F, message=F, include=FALSE}
library(tidyverse)
library(gt)

source("../lib/fmt_APA.R")
source("../lib/mcmc.R")
load("../data/export/paper_vars.RData")
load("../data/export/bayesian_effect_of_music_meditaiton_on_mw-bv-ae.RData")
mw_mus_med <- as.matrix(mod.mw.music_medi)
bv_mus_med <- as.matrix(mod.bv.music_medi)
ae_mus_med <- as.matrix(mod.ae.music_medi)

coef_hdi <- function(x){
  dir="+"
  m = fmt_APA_numbers( mean(x), .chr=T )
  # ll <- hdi(x)[1]
  # ul <- hdi(x)[2]
  ll  = fmt_APA_numbers( quantile(x, 0.025)[[1]], .chr=T )
  ul  = fmt_APA_numbers( quantile(x, 0.975)[[1]], .chr=T )
  erat = sum(x>0)/sum(x<=0)
  pval = sum(x>0)/length(x)

  if(m<0){
    erat=1./erat
    pval=1-pval
    dir="-"
  }
  if(is.infinite(erat)){
    erat=ifelse(erat<0, "-\\infty", "\\infty")
  } else {
    erat=erat
  }
  pval = fmt_APA_numbers(pval, .p=T)
  erat = fmt_APA_numbers(erat, .chr=T)

  sprintf(
    "$M=%s, [%s, %s], p^{%s}=%s, \\text{ER}^{%s}=%s$", 
    m, ll, ul, dir, pval, dir, erat)
}

```


# Reporting accumulating effects: 

## MW: 
```{r, include=FALSE}
acc_mw <- 
  as_tibble(mod.pfc.mw) |>
    mutate(
    .before = 1,
    diffB1_B0 = `b_stimulationreal:blockB1` - 0,
    diffB2_B1 = `b_stimulationreal:blockB2` - `b_stimulationreal:blockB1`,
    diffB3_B2 = `b_stimulationreal:blockB3` - `b_stimulationreal:blockB2`,
  ) |> as.matrix(x=_)
```
\n
B1-B0: `r coef_hdi( acc_mw[,"diffB1_B0"] )`   

\n
B2-B1: `r coef_hdi(acc_mw[,"diffB2_B1"])`   
\n
\n
B3-B2: `r coef_hdi(acc_mw[,"diffB3_B2"])`   
\n


## BV
```{r, include=FALSE}
acc_bv <-
  as_tibble(mod.pfc.bv) |>
    mutate(
    .before = 1,
    diffB1_B0 = `b_stimulationreal:blockB1` - 0,
    diffB2_B1 = `b_stimulationreal:blockB2` - `b_stimulationreal:blockB1`,
    diffB3_B2 = `b_stimulationreal:blockB3` - `b_stimulationreal:blockB2`,
  ) |> as.matrix(x=_)
```
\n
B1-B0: `r coef_hdi(acc_bv[,"diffB1_B0"])` 
\n 

B2-B1: `r coef_hdi(acc_bv[,"diffB2_B1"])` 
\n 

B3-B2: `r coef_hdi(acc_bv[,"diffB3_B2"])` 
\n


## AE
```{r, include=FALSE}
acc_ae <-
  as_tibble(mod.pfc.ae) |>
    mutate(
    .before = 1,
    diffB1_B0 = `b_stimulationreal:blockB1` - 0,
    diffB2_B1 = `b_stimulationreal:blockB2` - `b_stimulationreal:blockB1`,
    diffB3_B2 = `b_stimulationreal:blockB3` - `b_stimulationreal:blockB2`,
  ) |> as.matrix(x=_)
```

B1-B0: `r coef_hdi(acc_ae[,"diffB1_B0"])`  
\n

B2-B1: `r coef_hdi(acc_ae[,"diffB2_B1"])`  
\n

B3-B2: `r coef_hdi(acc_ae[,"diffB3_B2"])`  
\n




# Reporting the effect of music and meditaiton

```{r, include=FALSE}
coef_hdi <- function(x){
  dir="+"
  m = fmt_APA_numbers( mean(x), .chr=T )
  # ll <- hdi(x)[1]
  # ul <- hdi(x)[2]
  ll  = fmt_APA_numbers( quantile(x, 0.025)[[1]], .chr=T )
  ul  = fmt_APA_numbers( quantile(x, 0.975)[[1]], .chr=T )
  erat = sum(x>0)/sum(x<=0)
  pval = sum(x>0)/length(x)

  if(m<0){
    erat=1./erat
    pval=1-pval
    dir="-"
  }
  if(is.infinite(erat)){
    erat=ifelse(erat<0, "-\\infty", "\\infty")
  } else {
    erat=erat
  }
  pval = fmt_APA_numbers(pval, .p=T)
  erat = fmt_APA_numbers(erat, .chr=T)

  sprintf(
    "$b=%s, [%s, %s], p^{%s}=%s, \\text{ER}^{%s}=%s$", 
    m, ll, ul, dir, pval, dir, erat)
}
```


Our results did not find convincing evidence that musical or meditation experience influenced either MW, BV or AE. The findings revealed that neither musical (`r coef_hdi(mw_mus_med[,"b_music_year1"])`) or meditation (`r coef_hdi(mw_mus_med[,"b_meditation1"])`) experience influenced MW. Similarly, for BV, the results did not find convincing evidence that musical experience (`r coef_hdi(bv_mus_med[,"b_music_year1"])`) or meditation experience (`r coef_hdi(bv_mus_med[,"b_meditation1"])`) influenced BV. Lastly, for AE, the results did not indicate convincing evidence that musical experience (`r coef_hdi(ae_mus_med[,"b_music_year1"])`) or meditation experience (`r coef_hdi(ae_mus_med[,"b_meditation1"])`) influenced AE.  

